One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
edited the certification section (5 only)

A certificate shall attest a user the expertise in the covered skills.
Ensuring the integrity of a certificate is an important aspect, i.e., we must check that the learning outcomes of the covered skills are achieved and prevent self-cheating or dishonesty.

Students can always cheat an examination -- the risk depends on the type of exam and methods used for the assessment.
As we want to enable a cost-effective assessment (free for the practitioner), we chose an online examination.
This increases the opportunity for cheating \cite{rowe2004cheating} but we deploy several  strategies that aim to minimize the risk of self-cheating as raising awareness, a question pool, and delay.
Since knowledge can age, the month and year an examination took place is also indicated.
As certificates bundle multiple skills together as examination of a single fine-grained leaf-level skill would be too easy for short-term memorization and prone to self-cheating.
We believe the incentive to deliberately fake the assessment, e.g., by having the exam filled by someone else, and thus, being awarded a certificate is low.
Therefore, we address this only in a lightweight fashion.

A process has also been created for prospect contributors of examination questions.
The questions are the only proprietary component for the HPCCF using restrictive license terms for authors while we give credit to them.
We considered this necessary to minimize the establishment of solution databases; we omit further details here.

We discuss the prototypical process that we implemented for conducting examination in the following.

>>>>

A certificate shall serve as a confirmation that a user obtain the expertise in the relevant skills.
Special considerations needs to be given to the certification integrity.  
We must ensure that the learning outcomes of the covered skills are examined to a satisfactory degree, and prevent self-cheating or dishonesty.
Students can always cheat during an examination -- the susceptibility to cheating depends on many factors, including but not limited to the type of exam, methods used for assessment, motivation for taking it,  consequences of failing or scoring poorly, and the possibility and frequency of resits.

We want to enable a cost-effective assessment (free for the practitioner), so we chose an online examination.
This increases the opportunity for cheating \cite{rowe2004cheating} but we plan to deploy a several strategies to minimise the risk of cheating, such as raising the awareness of the examinees, using a pool of questions, and setting time limits for each question.

Since knowledge can age, each certificate needs to indicated when (month and year) the qualifying examination took place.
Also, because the examination of a single fine-grained leaf-level skill would be too easy for short-term memorisation and more prone to self-cheating, the certificates bundle multiple skills together.
We believe the incentive to deliberately fake the assessment, e.g., by having the exam filled by someone else, and thus, being awarded a certificate, is low.
Therefore, we address this issue in a lightweight fashion only.

A process has also been created for prospective contributors of the examination questions.
The questions are the only proprietary component for the HPCCF -- using restrictive license terms for authors while giving them credit. 
This is considered necessary to minimise the overhead of managing the database containing solutions to the examination questions.

In the next section, we discuss the process proposed for conducting the examination.
